\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
In figure \ref{fig:HeleShawHeter_VR10}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case there are  two different mobility ratios of $3$ and $10$ while for the heterogeneous case only the case of  mobility ratio of $10$ will be investigated.

>>>>

\medskip
In order to investigate the impact of medium heterogeneity on formation and growth of viscous fingers, a numerical simulation was conducted using a distribution of permeability ({\bf K}) ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy).

In figure \ref{fig:HeleShawHeter_VR10}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case there are  two different mobility ratios of $3$ and $10$ while for the heterogeneous case only the case of  mobility ratio of $10$ will be investigated.
